\documentclass[10pt, letterpaper]{article}

% -------------------- Preamble --------------------
\usepackage[
    ignoreheadfoot,
    top=0.65cm,
    bottom=0.65cm,
    left=1.0cm,
    right=1.0cm
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{paracol}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\titleformat{\section}{\needspace{3\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.1cm}{0.05cm}

\renewcommand\labelitemi{\small$\bullet$}

% -------------------- Custom Environments --------------------
\newenvironment{highlights}{
    \begin{itemize}[topsep=0pt, itemsep=1pt, leftmargin=10pt]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0cm}{0cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2]{
    \onecolentry
    \setcolumnwidth{\fill,4.2cm}
    \begin{paracol}{2}
    #1
    \switchcolumn
    \raggedleft #2
}{
    \end{paracol}
    \endonecolentry
}

% -------------------- Document --------------------
\begin{document}

% -------------------- Header --------------------
\begin{center}
    {\fontsize{24pt}{24pt}\selectfont \textbf{Roki Roy}} \\[4pt]
    \href{https://royroki.github.io/wowfy}{Portfolio} \textbullet\ 
    \href{https://github.com/royroki}{github.com/royroki} \textbullet\ 
    \href{https://linkedin.com/in/rokiroy}{linkedin.com/in/rokiroy} \\ 
    \href{mailto:rokiroydev@gmail.com}{rokiroydev@gmail.com} \textbullet\ 
    +91 9800 881 300 \textbullet\ Siliguri
\end{center}

% -------------------- Summary --------------------
\section{Summary}
\begin{onecolentry}
\begin{highlights}
\item Full-stack developer with production experience building Flutter, React, and Golang systems used by 5,000+ users. Strong focus on clean architecture, backend performance, and shipping real-world products across web, mobile, and wearables. Proven ability to deliver and maintain production systems end-to-end in fast-paced Agile environments.
\end{highlights}
\end{onecolentry}

% -------------------- Experience --------------------
\section{Experience}

\begin{twocolentry}{
\textbf{SDE 1}, \href{https://fordelstudios.com}{Fordel Studios} $\cdot$ Onsite
}{
Feb 2025 -- Present
}
\end{twocolentry}

\begin{onecolentry}
\begin{highlights}
\item Led end-to-end Flutter app development using clean architecture, supporting 5,000+ active users with 98\% crash-free sessions.
\item Designed and implemented Golang backend services, reducing API response time by 25\% and improving system reliability.
\item Collaborated with design, backend, and QA teams to architect, implement, and ship features within Agile sprints.
\item Accelerated a React--Node.js e-commerce platform by integrating 5+ third-party APIs, reducing page load times by 30\% and improving conversion rate by 12\%.
\item Designed and shipped a companion Apple Watch app in Swift, extending core mobile functionality to wearable platforms.
\end{highlights}
\end{onecolentry}

\begin{twocolentry}{
\textbf{Full Stack Developer Intern}, \href{https://fordelstudios.com}{Fordel Studios} $\cdot$ Onsite
}{
Aug 2024 -- Jan 2025
}
\end{twocolentry}

\begin{onecolentry}
\begin{highlights}
\item Refactored 15+ backend APIs and database queries, cutting average response times by 40\% and enabling 8 new frontend features.
\end{highlights}
\end{onecolentry}

% -------------------- Projects --------------------
\section{Projects}

\href{https://play.google.com/store/apps/details?id=com.emudhra.emSigner&hl=en_IN}{\textbf{emSigner Digital Signature}} \\
\begin{highlights}
\item Developed a production Flutter application integrating PayU, Stripe payment gateways and Aadhaar verification services, achieving 98\% crash-free sessions across 5,000+ active users.
\item Architected clean architecture patterns across 20+ feature modules to support scalable development and reduce technical debt by 35\%.
\item \textbf{Stack:} Flutter, Dart, REST API, Android, iOS
\end{highlights}

\href{https://theformulashop.com/}{\textbf{The Formula Shop -- Production E-commerce Platform}} \\
\begin{highlights}
\item Launched and shipped a production e-commerce platform serving 1,200+ monthly active users and processing 500+ orders.
\item Delivered product catalog (300+ SKUs), cart, and checkout flows with client-side rendering, achieving sub-2s page loads.
\item Integrated third-party services for payments and order processing.
\item \textbf{Stack:} Next.js, Tailwind CSS, REST APIs
\end{highlights}

\href{https://www.astraterra.ae/}{\textbf{Astra Terra Properties}} \\
\begin{highlights}
\item Developed a full-stack real estate platform with map-based search across 200+ properties, advanced filtering (8 parameters), and optimized rendering.
\item Integrated Leaflet Maps, GSAP animations, and Firebase backend for real-time data synchronization with sub-500ms latency.
\item \textbf{Stack:} Next.js, TypeScript, GSAP, Leaflet Maps, Firebase
\end{highlights}

\href{https://github.com/RoyRoki/LetsGo}{\textbf{LetsGo -- Tag-Based Chat System}} \\
\begin{highlights}
\item Engineered a tag-based user matching system using Redis Bitmaps and Lua scripting for low-latency user discovery.
\item Engineered a real-time WebSocket chat server handling 100+ concurrent connections with gRPC-based microservice communication.
\item Containerized 3-service system using Docker Compose with automated deployment workflows, reducing setup time by 70\%.
\item \textbf{Stack:} Go 1.22, gRPC, Redis + Lua, WebSockets, Docker, TypeScript
\end{highlights}

% -------------------- Technologies --------------------
\section{Technologies}
\begin{onecolentry}
\textbf{Backend \& Systems:} Golang, PostgreSQL, Docker, gRPC \\
\textbf{Frontend:} Next.js, React, TypeScript, JavaScript (ES6+) \\
\textbf{Mobile:} Flutter (Dart), Swift \\
\textbf{Cloud \& Tools:} Firebase, AWS \\
\textbf{Agentic \& Automation:} Agentic workflows, LLM tool-calling, task automation, AI-assisted development
\end{onecolentry}

% -------------------- Education --------------------
\section{Education}

\begin{twocolentry}{
\textbf{University of North Bengal} --- Bachelor of Computer Applications (BCA)
}{
Expected May 2027
}
\end{twocolentry}

{\small\textit{Relevant Coursework: Data Structures, Database Management Systems, Operating Systems, Computer Networks}}

\end{document}
