\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=0.6cm,
    bottom=0.6cm,
    left=1.0cm,
    right=1.0cm
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.08cm}{0.2cm}

\renewcommand\labelitemi{\small$\bullet$}

\newenvironment{tightitem}{
    \begin{itemize}[topsep=0pt, itemsep=0pt, parsep=0.3pt, leftmargin=10pt]
}{
    \end{itemize}
}

\begin{document}

% ---------------- Header ----------------
\begin{center}
{\fontsize{22pt}{22pt}\selectfont \textbf{Roki Roy}} \\[3pt]
Backend Developer \\[3pt]
\href{https://royroki.github.io/wowfy}{Portfolio} \textbullet\
\href{https://github.com/royroki}{GitHub} \textbullet\
\href{https://linkedin.com/in/rokiroy}{LinkedIn} \\
rokiroydev@gmail.com \textbullet\ +91 9800 881 300 \textbullet\ Siliguri, India
\end{center}

% ---------------- Summary ----------------
\section{Summary}

Backend-focused engineer with production experience building Go-based REST APIs, authentication systems, and scalable backend services. Capable of delivering full-stack solutions using React, Next.js, and Flutter. Strong foundation in clean architecture, database design, API integration, and Docker-based deployment.

% ---------------- Experience ----------------
\section{Experience}

\textbf{Software Development Engineer (SDE 1)} — Fordel Studios \hfill Feb 2025 -- Present  
\begin{tightitem}
\item Implemented and integrated Golang REST APIs for production web and mobile applications.
\item Integrated third-party services including payment gateways and verification APIs.
\item Optimized PostgreSQL queries through indexing and schema improvements.
\item Contributed to Flutter and React feature development in Agile sprints.
\end{tightitem}

\textbf{Full Stack Developer Intern} — Fordel Studios \hfill Aug 2024 -- Jan 2025  
\begin{tightitem}
\item Refactored backend APIs and improved database query structures.
\item Built additional endpoints supporting new frontend features.
\item Assisted in debugging and maintaining production issues.
\end{tightitem}

% ---------------- Key Projects ----------------
\section{Key Projects}

\href{https://github.com/RoyRoki/Dooars_Dil}{\textbf{Dooars Dil — Location-Based Dating Application (Personal)}}  
\begin{tightitem}
\item Developed backend services for user authentication, profile management, and location-based matching in Go.
\item \textbf{Challenge:} Handling hyper-local matchmaking efficiently, filtering active users in real-time, and supporting low-latency voice-first interactions.
\item \textbf{Solution:} Designed a highly optimized relational schema with PostGIS for specific town clusters instead of expensive generic radius queries.
\item \textbf{Implementation:} Built a concurrent voice-first messaging architecture supporting real-time voice notes, utilizing goroutines for async audio processing and efficient database connection pooling.
\item Stack: Go, PostgreSQL, PostGIS, REST APIs
\end{tightitem}

\href{https://github.com/RoyRoki/AI-CREATIVE-CONTENT-GENERATOR}{\textbf{ZenliAI — AI Content Platform (Freelance)}}  
\begin{tightitem}
\item Architected a scalable Go backend using clean architecture principles with dependency injection and repository patterns.
\item \textbf{Challenge:} Managing long-running generative AI API calls, merging multi-modal responses, generating complex PDFs, and tracking user token credits accurately without blocking UI threads.
\item \textbf{Solution:} Implemented a robust asynchronous job queue and worker pool using Redis and Asynq for non-blocking content generation and background task management.
\item \textbf{Implementation:} Integrated transactional database operations to guarantee ACID compliance during credit deductions and handled WebSocket events for real-time progress updates to the React frontend.
\item Stack: Go, PostgreSQL, Redis (Asynq queue), Docker, WebSockets
\end{tightitem}

\href{https://github.com/RoyRoki/vayuroom}{\textbf{Vayuroom — WebRTC Platform (Personal)}}  
\begin{tightitem}
\item Developed peer-to-peer WebRTC video conferencing system with Firebase as the ephemeral signaling server.
\item \textbf{Challenge:} Establishing secure chat and video call encryption across multiple peers without routing traffic through a central vulnerable media server.
\item \textbf{Solution:} Implemented a zero-knowledge, end-to-end encrypted architecture using WebRTC Data Channels and DTLS-SRTP protocols.
\item \textbf{Implementation:} Designed a custom mesh-networking routing algorithm for small-group P2P calls, ensuring cryptographic keys are exchanged out-of-band and never stored persistently.
\item Stack: React, WebRTC, Firebase, Cryptography (E2EE), Mesh Networking
\end{tightitem}



% ---------------- Skills ----------------
\section{Technical Skills}

\textbf{Backend:} Go (goroutines, channels), REST APIs, JWT, Redis, PostgreSQL (schema design, indexing) \\
\textbf{Familiar With:} React, Next.js, TypeScript, Flutter, Swift \\
\textbf{DevOps:} Docker, Firebase, AWS (basic), Git \\
\textbf{Concepts:} Clean Architecture, Concurrency, API Integration, Database Design

% ---------------- Education ----------------
\section{Education}

\textbf{University of North Bengal} — BCA \hfill Expected May 2026

\end{document}
