\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=0.6cm,
    bottom=0.6cm,
    left=1.0cm,
    right=1.0cm
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.08cm}{0.04cm}

\renewcommand\labelitemi{\small$\bullet$}

\newenvironment{tightitem}{
    \begin{itemize}[topsep=1pt, itemsep=1pt, leftmargin=10pt]
}{
    \end{itemize}
}

\begin{document}

% ---------------- Header ----------------
\begin{center}
{\fontsize{22pt}{22pt}\selectfont \textbf{Roki Roy}} \\[3pt]
Mobile Engineer (Flutter, Swift, iOS, Android) \\[3pt]
\href{https://royroki.github.io/wowfy}{Portfolio} \textbullet\
\href{https://github.com/royroki}{GitHub} \textbullet\
\href{https://linkedin.com/in/rokiroy}{LinkedIn} \\
rokiroydev@gmail.com \textbullet\ +91 9800 881 300 \textbullet\ Siliguri, India
\end{center}

% ---------------- Summary ----------------
\section{Summary}

Mobile application developer with production experience building high-performance cross-platform and native apps. Expert in Flutter for multi-platform delivery and Swift for native iOS/WatchOS experiences. Proven track record of shipping apps with 5,000+ active users, implementing clean architecture, and integrating complex device features like Bluetooth, Biometrics, and Background Services.

% ---------------- Experience ----------------
\section{Experience}

\textbf{Software Development Engineer (SDE 1)} — Fordel Studios \hfill Feb 2025 -- Present  
\begin{tightitem}
\item Led end-to-end Flutter app development, achieving 98\% crash-free sessions for 5,000+ users.
\item Architected a scalable mobile codebase using Clean Architecture and BLoC pattern.
\item Designed and shipped a native Apple Watch companion app using SwiftUI to extend core features.
\item Integrated complex native modules (biometrics, file system) into Flutter via platform channels.
\end{tightitem}

\textbf{Full Stack Developer Intern} — Fordel Studios \hfill Aug 2024 -- Jan 2025  
\begin{tightitem}
\item Optimised mobile app performance, reducing startup time by 40%.
\item Implemented offline-first features and background data synchronization.
\end{tightitem}

% ---------------- Key Projects ----------------
\section{Key Projects}

\href{https://play.google.com/store/apps/details?id=com.emudhra.emSigner&hl=en_IN}{\textbf{emSigner — Digital Signature Platform}}  
\begin{tightitem}
\item Developed a production Flutter application integrating PayU, Stripe payment gateways and Aadhaar verification services.
\item Reduced technical debt by 35\% by refactoring monolithic code into modular Clean Architecture.
\item Stack: Flutter, Dart, Android, iOS, REST APIs
\end{tightitem}

\href{https://apps.apple.com/jp/app/emsigner-sign-electronically/id1246670687?l=en-US&platform=watch}{\textbf{emSigner Companion App — Apple Watch}}  
\begin{tightitem}
\item Built a native WatchOS companion app extending digital signature workflows to wearables.
\item Implemented independent WatchOS networking and secure data sync with the main iOS app.
\item Stack: Swift, SwiftUI, WatchOS
\end{tightitem}

\href{https://github.com/RoyRoki/Dooars_Dil}{\textbf{Dooars Dil — Hyperlocal Dating App}}  
\begin{tightitem}
\item Engineered a voice-first dating experience with audio profile recording and playback.
\item Implemented real-time location-based matching using Flutter and Google Maps/Mapbox integrations.
\item Stack: Flutter, Dart, Riverpod, Audio Players, Real-time location
\end{tightitem}

\textbf{Tournament Management App}  
\begin{tightitem}
\item Developed a cross-platform tournament management system for organizing local sports events.
\item Built using Capacitor to deploy a single web codebase to both Android and iOS.
\item Stack: Capacitor, JavaScript, Mobile Web
\end{tightitem}

% ---------------- Skills ----------------
\section{Technical Skills}

\textbf{Mobile Development:} Flutter (Dart), Swift (iOS/WatchOS), Capacitor, Android (Kotlin basics) \\
\textbf{Architecture \& State:} Clean Architecture, BLoC, Riverpod, Provider, MVC/MVVM \\
\textbf{Native Integration:} Platform Channels, Bluetooth Low Energy (BLE), Biometrics, Background Services \\
\textbf{Tools:} Xcode, Android Studio, Firebase, Fastlane, CI/CD for Mobile \\
\textbf{Backend Familiarity:} Go, Node.js, REST APIs

% ---------------- Education ----------------
\section{Education}

\textbf{University of North Bengal} — BCA \hfill Expected May 2026

\end{document}
