\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=0.6cm,
    bottom=0.6cm,
    left=1.0cm,
    right=1.0cm
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.08cm}{0.04cm}

\renewcommand\labelitemi{\small$\bullet$}

\newenvironment{tightitem}{
    \begin{itemize}[topsep=1pt, itemsep=1pt, leftmargin=10pt]
}{
    \end{itemize}
}

\begin{document}

% ---------------- Header ----------------
\begin{center}
{\fontsize{22pt}{22pt}\selectfont \textbf{Roki Roy}} \\[3pt]
Frontend Engineer (Next.js, 3D Web, High-Performance UI) \\[3pt]
\href{https://royroki.github.io/wowfy}{Portfolio} \textbullet\
\href{https://github.com/royroki}{GitHub} \textbullet\
\href{https://linkedin.com/in/rokiroy}{LinkedIn} \\
rokiroydev@gmail.com \textbullet\ +91 9800 881 300 \textbullet\ Siliguri, India
\end{center}

% ---------------- Summary ----------------
\section{Summary}

Frontend-focused engineer specializing in building high-performance, interactive web experiences using Next.js, React, and GSAP. Expert in crafting complex admin dashboards, immersive 3D web applications, and responsive e-commerce platforms. Deep understanding of modern CSS, animation libraries, and state management for scalable production applications.

% ---------------- Experience ----------------
\section{Experience}

\textbf{Software Development Engineer (SDE 1)} — Fordel Studios \hfill Feb 2025 -- Present  
\begin{tightitem}
\item Led frontend development for high-traffic web applications using Next.js and Tailwind CSS.
\item integrated complex third-party APIs (Payment Gateways, Maps) into seamless UI flows.
\item Optimized core web vitals and rendering performance, reducing LCP by 40\%.
\item Collaborated with designers to implement pixel-perfect, responsive UI components.
\end{tightitem}

\textbf{Full Stack Developer Intern} — Fordel Studios \hfill Aug 2024 -- Jan 2025  
\begin{tightitem}
\item Built and deployed responsive frontend features for production e-commerce platforms.
\item Refactored legacy React codebases to use modern hooks and state management patterns.
\end{tightitem}

% ---------------- Key Projects ----------------
\section{Key Projects}

\href{https://we-care-packages-admin.vercel.app/}{\textbf{We Care Packages — Travel Agency Admin Panel}}  
\begin{tightitem}
\item Architected a comprehensive admin dashboard for managing travel packages, bookings, and user data.
\item Implemented complex data grids with sorting, filtering, and bulk actions using React Table.
\item Designed role-based access control (RBAC) and secure authentication flows.
\item Stack: Next.js, Tailwind CSS, TypeScript, REST APIs
\end{tightitem}

\href{https://pathsathi.vercel.app/}{\textbf{PathSathi — Immersive Travel Storytelling Platform}}  
\begin{tightitem}
\item Developed a scroll-driven storytelling experience for travel routes using GSAP and Lenis for smooth scrolling.
\item Created interactive 3D map integrations and scroll-triggered animations to enhance user engagement.
\item Optimized asset loading and animation performance for 60fps experiences on mobile devices.
\item Stack: Next.js 14, GSAP, Framer Motion, Firebase, Tailwind CSS
\end{tightitem}

\href{https://theformulashop.com/}{\textbf{The Formula Shop — Production E-commerce Platform}}  
\begin{tightitem}
\item Shipped a full-featured e-commerce platform with 300+ SKUs and dynamic cart management.
\item Implemented client-side caching and optimistic UI updates for instant interactions.
\item Achieved sub-2s page loads and 90+ Lighthouse performance scores.
\item Stack: Next.js, Tailwind CSS, Redux Toolkit
\end{tightitem}

\href{https://www.astraterra.ae/}{\textbf{Astra Terra Properties — Real Estate Platform}}  
\begin{tightitem}
\item Built a map-based real estate search engine with advanced filtering and dynamic clustering.
\item Integrated Leaflet Maps with custom markers and GSAP transitions for property cards.
\item Stack: Next.js, TypeScript, GSAP, Leaflet Maps
\end{tightitem}

\href{https://rokiroy.in}{\textbf{Wowfy — 3D Interactive Portfolio}}  
\begin{tightitem}
\item Designed and developed an immersive 3D portfolio website showcasing projects and skills.
\item Utilized Three.js/React Three Fiber for interactive 3D elements and scene management.
\item Stack: React, Three.js, React Three Fiber, Framer Motion
\end{tightitem}

% ---------------- Skills ----------------
\section{Technical Skills}

\textbf{Frontend Code:} React.js, Next.js (App Router), TypeScript, JavaScript (ES6+), HTML5, CSS3 \\
\textbf{Styling \& UI:} Tailwind CSS, SCSS, Framer Motion, GSAP (ScrollTrigger), CSS Modules, Shadcn UI \\
\textbf{State Management:} Redux Toolkit, Zustand, React Context API \\
\textbf{Tools \& Performance:} Webpack, Vite, Figma-to-Code, Responsive Design, Web Vitals Optimization \\
\textbf{Backend Familiarity:} Golang, Node.js, Firebase, REST APIs

% ---------------- Education ----------------
\section{Education}

\textbf{University of North Bengal} — BCA \hfill Expected May 2026

\end{document}
